### 2021-05-24 ms/suppmat.tex
Add prior sensitivity tests

% Macros
\newcommand{\So}{$S_{1}$\xspace}
\newcommand{\St}{$S_{2}$\xspace}
\newcommand{\Pg}{$P_r$\xspace}
\newcommand{\Linf}{$L_{\infty}$}
\newcommand{\DWinf}{$DW_{\infty}$}
\newcommand{\alphat}{$\tilde{\alpha}$}
\newcommand{\lamat}{$l_{\alpha_{mat}}$}
\newcommand{\lamatb}{$l_{\alpha_{mat}}b$}
\newcommand{\rmax}{$r_{max}$\xspace}
\newcommand{\ageratio}{$\alpha_{mat}/\alpha_{max}$}
\newcommand{\yr}{year\textsuperscript{-1}}
\newcommand{\rsq}{$R^2$\xspace}
% Select what to do with command \comment:
\newcommand{\comment}[1]{}  % comment not shown
%\newcommand{\comment}[1]{\par {\bfseries \color{blue} #1 \par}} % comment shown
%% END MACROS SECTION

@@

% \begin{figure}[htbp] \centering
%     \includegraphics[width=0.9\linewidth]{simul_timeseries_declining.pdf} \caption{Simulated
%         time series of returning adult salmon abundance in the six scenarios. The lines denote the
%     simulated abundance estimates without observation error while the points are the same estimates
% including observation error.}
% \label{fig:simul-ts-dec}
% \end{figure}

% \begin{figure}[htbp] \centering
%     \includegraphics[width=0.95\linewidth]{sir_out_18_declining.pdf} \caption{Yearly
%         estimated \So, \St, and \Pg values in the six scenarios. True values
%         are denoted by blue circles, black circles show median estimates,
%         error bars indicate the 25\% and 75\% quantiles.}
% \label{fig:sir-out-dec}
% \end{figure}

% \begin{figure}[htbp] \centering
%     \includegraphics[width=0.7\linewidth]{simul_plots_6_declining.pdf}
%     \caption{Comparison of estimated and true \So values in the six
%         scenarios. True \So values are deterministic, black circles show
%         median \So estimates, error bars indicate the  25\% and 75\%
%         quantiles, while the blue line denotes a linear model fit of the
%         medians. The one-to-one relationship is shown by the gray dashed
%         line.}
% \label{fig:simul-six-plots-dec}
% \end{figure}

%\clearpage
%\subsection*{References}
\nobibliography{subset}

>>>>

% Macros
\newcommand{\So}{$S_{1}$\xspace}
\newcommand{\St}{$S_{2}$\xspace}
\newcommand{\Pg}{$P_g$\xspace}
\newcommand{\prmu}{$\mu_{Pg,r}$\xspace}
\newcommand{\Linf}{$L_{\infty}$}
\newcommand{\DWinf}{$DW_{\infty}$}
\newcommand{\alphat}{$\tilde{\alpha}$}
\newcommand{\lamat}{$l_{\alpha_{mat}}$}
\newcommand{\lamatb}{$l_{\alpha_{mat}}b$}
\newcommand{\rmax}{$r_{max}$\xspace}
\newcommand{\ageratio}{$\alpha_{mat}/\alpha_{max}$}
\newcommand{\yr}{year\textsuperscript{-1}}
\newcommand{\rsq}{$R^2$\xspace}
% Select what to do with command \comment:
\newcommand{\comment}[1]{}  % comment not shown
%\newcommand{\comment}[1]{\par {\bfseries \color{blue} #1 \par}} % comment shown
%% END MACROS SECTION

@@

\subsection*{Posterior estimates with weaker priors}

To assess the sensitivity of our model parameter estimates to the choice of
priors, we assessed posterior estimate under two weaker prior scenarios:
one with wider priors for \So, \St (Fig.~\ref{fig:zweak}), and a second one with wide priors
of \prmu for all populations regardless of whether they were considered
1SW-dominated or not (Fig.~\ref{fig:prweak}).

\begin{figure}[htbp] \centering
    \includegraphics[width=0.55\linewidth]{figures/z-weak-prior.png}
    \caption{Priors used for marine survival of one sea-winter (\So) and two
        sea-winter (\St) returns. Solid lines denote strong priors used in the
        study, while dotted lines denote weaker priors used to assess
        sensitivity to prior choice.} \label{fig:zweak} \end{figure}

\begin{figure}[htbp] \centering
    \includegraphics[width=0.55\linewidth]{figures/pr-weak-prior.png}
    \caption{Prior of the probability of returning as 1SW for all populations
        under the weak \prmu prior scenario. Note this prior is identical to
        that used in the study for non 1SW-dominated populations.}
    \label{fig:prweak} \end{figure}

The model runs with weaker priors did not differ mayorly from those with
stronger priors, particularly for posterior estimates of \So, which show the
same overall trends for all populations and some yearly \So estimates with
high uncertainty (i.e., large error bars) show greater uncertainty uncertainty
under the weak \So and \St scenario (Fig.~\ref{fig:s1-trends-priors}).
Not unexpectedly, the weak \Pg scenario had no visually discernible effect on
posterior estimates of \So.

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/s1-trends-priors.png}
    \caption{Median posterior estimates of survival in the first year at sea
        (\So) for the seven populations examined under three scenarios with
        different priors. The strong prior scenario is the one presented in
        our study, the weak \Pg priors uses the same weak prior for all
        populations as shown by Fig.~\ref{fig:prweak}, while the weak \So \&
        \St scenario used wider survival priors as shown in Fig.~\ref{fig:zweak}.} 
    \label{fig:s1-trends-priors} \end{figure}

Having weaker \So and \St priors did considerable widen the posterior
estimates of \St for all populations (Fig.~\ref{fig:s2-trends-priors}). The
Saint-Jean River, which had the least uncertain \St estimates among all
populations, had considerably larger uncertainties in \St while still
maintaining a very similar temporal trend in \St. The Trinité River also
maintained a similar temporal trend in \St, but the weaker priors resulted in
annual estimates of \St showing a larger spread, particularly in 1994 and 1995
which were the years withe highest estimated \St.

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/s2-trends-priors.png}
    \caption{Median posterior estimates of survival in the second year at sea
        (\St) for the seven populations examined under three scenarios with
        different priors. The strong prior scenario is the one presented in
        our study, the weak \Pg priors uses the same weak prior for all
        populations as shown by Fig.~\ref{fig:prweak}, while the weak \So \&
        \St scenario used wider survival priors as shown in Fig.~\ref{fig:zweak}.} 
    \label{fig:s2-trends-priors} \end{figure}

Estimates of \Pg under the weak \Pg scenario look almost identical to those
under the strong priors scenario, however the weak \So and \St scenario
resulted in more uncertain \Pg estimates for non 1SW-dominated populations
(Fig.~\ref{fig:pr-trends-priors}). For these populations, the temporal trends
observed in the strong prior scenario were maintained under the weak \So and
\St scenario, albeit weakened by the larger uncertainties in annual \Pg
estimates.

Overall, weakening the \prmu priors did not have an observable effect on model
parameter estimates, while weakening \So and \St did result in more uncertain
estimates of \St and \Pg, with estimates of \So being mostly unchanged.

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/pr-trends-priors.png}
    \caption{Median posterior estimates of proportion returning after one winter at sea 
        (\Pg) for the seven populations examined under three scenarios with
        different priors. The strong prior scenario is the one presented in
        our study, the weak \Pg priors uses the same weak prior for all
        populations as shown by Fig.~\ref{fig:prweak}, while the weak \So \&
        \St scenario used wider survival priors as shown in Fig.~\ref{fig:zweak}.} 
    \label{fig:pr-trends-priors} \end{figure}

We calculated the correlations of estimated trends in $Z_1$ among populations
under the weak \So and \St scenario. While the direction of the correlation
stayed the same between all populations when compared with the strong prior
scenario, there were differences in the correlation coefficients (Fig.~\ref{fig:s1-corr-weakz}).
Among these, the correlation coefficients differed significantly for three pair-wise
comparisons: the correlations between Campbellton and Nashwaak as well
Campbellton and Trinité changed from non-significant to positively
significant, while the correlation between LaHave and Saint-Jean changed from negatively significant to
non-significant even though the coefficient value decreased further into the
negative.
Twelve out of the 21 pair-wise correlations were significant (p-value below 0.05) yet under the  
weak \So and \St scenario 9 out of the twelve significant correlations were positive.

\begin{figure}[htbp] \centering
    \includegraphics[width=0.95\linewidth]{figures/corrplot-post-z1-corrected-weakz.png} \caption{
        Correlations of estimated trends in $Z_1$ among populations with weak \So and
\St priors. Correlation coefficients are shown in each square, while colouring
        denotes significance of the correlation ($p \leq 0.05$) as well as the direction and magnitude.}
\label{fig:s1-corr-weakz}
\end{figure}

%\clearpage
%\subsection*{References}

\nobibliography{subset}
